---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Markdown text has formatting directives

## Lists

I am creating lists. More text here.  *This is italic*

### List one

This is a numbered list

1. number one
2. number two
3. number three

### List two

This is a fruit list

1. banana
2. apple
3. strawberry

[Link text](http://nceas.ucsb.edu)

$\sum {n+1}$

```{r}
library(readr)
```

# Introduction

This dataset came from here [link] (https://doi.org/10.18739/A25T3FZ8X)

* read in data

```{r chunk1, message=FALSE}
bg_chem <- read_csv("BGchem2008data.csv")
```


# Analysis

* calculate summary statistics

We are interested in nutrient concentrations over the whole water column, so we calculate the mean value of nutrients of interest

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)
```


* calculate mean Redfield ratio

```{r}
ratio <- (nitrate + nitrite + amm)/phos
ratio
```

We calculated the redfield ratio to be `r round(ratio) `


* plot Redfield ratio 

```{r}
plot(bg_chem$P, bg_chem$NO2 + bg_chem$NO3 + bg_chem$NH4)
```

